A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2019-01-13 article/02_Materials_and_Methods.Rmd
changes in simulation paramaters

$$
m_i = 
  \begin{dcases*} 
    0 & Figure \ref{simulation} AB, no intergroup exchange \\ 
    0.01 & Figure \ref{simulation} CD \\
    0.1 & Figure \ref{simulation} EF \\
    0.5 & Figure \ref{simulation} GH, very high exchange
  \end{dcases*}
$$

>>>>

$$
m_i = 
  \begin{dcases*} 
    0 & Figure \ref{simulation} AB, no intergroup exchange \\ 
    0.05 & Figure \ref{simulation} CD \\
    0.5 & Figure \ref{simulation} EF, very high exchange
  \end{dcases*}
$$
